Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-06-26 paper/structureScene.tex
typo
delete paragraph on dimensionality to fit 10 pages

Finally, the SVM can also be extended to handle nonlinear decision surfaces. This is obtained using the ``kernel trick'', which exploits the fact that all calculations in the SVM rely only on the inner product between vectors. By replacing this standard inner product by some other positive definite symmetric mapping, such as a Gaussian radial basis function (RBF), this is equivalent to performing a linear SVM after mapping the feature vectors into some high-dimensional space. A nonlinear mapping then results in a nonlinear decision surface in the orignal space.

@@

While the scattering coefficients have higher dimension compared to the MFCCs, this does not necessarily imply higher performance. Indeed, if the sounds to be classified were completely classified by their spectral envelopes, MFCCs would be sufficient and may even outperform the scattering transforms, since in this case the latter would contain superfluous modulation information. The results above, however, show the opposite tendency, where this additional information does in fact improve results.

>>>>

Finally, the SVM can also be extended to handle nonlinear decision surfaces. This is obtained using the ``kernel trick'', which exploits the fact that all calculations in the SVM rely only on the inner product between vectors. By replacing this standard inner product by some other positive definite symmetric mapping, such as a Gaussian radial basis function (RBF), this is equivalent to performing a linear SVM after mapping the feature vectors into some high-dimensional space. A nonlinear mapping then results in a nonlinear decision surface in the original space.

@@
